---
title: 'MIE237'
author: "Neil Montgomery"
date: "2016-04-05"
output: 
  ioslides_presentation: 
    css: 'styles.css' 
    widescreen: true 
    transition: 0.001
---
\newcommand{\Var}[1]{\text{Var}\left( #1 \right)}
\newcommand{\E}[1]{E\left( #1 \right)}
\newcommand{\Sample}[1]{#1_1,\ldots,#1_n}
\newcommand{\od}[2]{\overline #1_{#2\cdot}}
\newcommand{\flist}[2]{\{#1_1, #1_2, \ldots, #1_#2\}}
\newcommand{\samp}[2]{#1_1, #1_2, \ldots, #1_#2}
\renewcommand{\bar}[1]{\overline{#1}}
\newcommand{\ve}{\varepsilon}
\newcommand{\bs}[1]{\boldsymbol{#1}}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
```

## Example 1 - unintentially challenging!

```{r, echo=TRUE}
set.seed(12)
n <- 50
x1 <- runif(n)
x2 <- runif(n)
x3 <- runif(n)
x4 <- runif(n)
x5 <- runif(n)
y <- x1 + 0.4*x2 + 0.6*x4 + rnorm(n, 0, 0.2)
f1 <- data.frame(y,x1,x2,x3,x4,x5)
```

But according to the forward strategy, all variables get included. 

It turns out this happened by sheer chance (about 3 out of 1000 chance).

## Otherwise example 1 was straightforward

```{r, echo=FALSE, warning=FALSE, fig.height=5.5, fig.width=9, fig.align='center'}
library(GGally)
ggpairs(f1)
```


## Example 2

```{r, echo=TRUE}
library(rio)
f2 <- import("problem.xlsx")
```

## Ex 2 correlations

```{r, echo=FALSE, warning=FALSE, fig.height=5.5, fig.width=9, fig.align='center'}
library(GGally)
ggpairs(f2)
```

## True model Ex 2

$$y = 1 + 0.5x_1 + 0.1x_2 + 0.3 x_3 +0.4x_4+0.5x_5 + \varepsilon$$

The $x$ variables were created from a $5^d$ normal distribution with
some correlations put in.

The model fitting procedure doesn't end up with the ``truth'' in this case.



